Classification of RDF Constraint Types Ensuring High Quality of Metadata and Data

### 2015-04-27 paper/paper7/paper7.tex
abstract

\begin{abstract}
For research institutes, data libraries, and data archives,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world.
%The data most often used in research within the community around research data for the social, behavioural, and economic sciences (\emph{SBE}) is person-level data, i.e., data collected about individuals (households, businesses). 
%%The DDI-RDF Discovery Vocabulary is used to describe and to discover this kind of research data.
%While performing research, the detailed, often access restricted person-level
%data is aggregated into less confidential publicly available multi-dimensional tables which answer particular research questions and whose purpose is to gain an interest in further more detailed analyses on the underlying person-level data.
To ensure high quality and trust, metadata and data must satisfy certain criteria - specified in terms of RDF constraints. 
%From 2012 to 2015 together with other Linked Data community members and \emph{SBE} experts, we developed diverse vocabularies to represent \emph{SBE} metadata and data in RDF.

In this paper, we propose a system to classify RDF constraints and RDF constraint types, which in most cases correspond to RDF validation requirements.
Constraints are instantiated from constraint types in order to validate both metadata and data independently from used vocabularies. 
Within the context of a complex and complete real world running example within the community around research data for the \emph{social, behavioural, and economic (SBE) sciences}, we prove the claim that the developed classification system perfectly applies for diverse vocabularies.
We show how data in rectangular format and metadata on person-level or more generally record-unit data sets (i.e., data about individuals, households, businesses), aggregated data sets, thesauri, and statistical classifications are represented in RDF and how therefore reused vocabularies are interrelated.
We explain how \emph{SBE} (meta)data is validated against constraints to ensure high quality and trust.
We exhaustively evaluated the metadata quality of large real world aggregated, person-level, and thesauri data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of constraint types.

\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Rectangular Data, SKOS, XKOS, Linked Data, Semantic Web}
\end{abstract}

@@

%\tb{terminology: data in singular form / data set - NOT dataset / person-level data - NOT microdata / study - NOT survey}
\tb{DCAT und XKOS nur in future work}
For more than a decade, members of the community around research data for the \emph{social, behavioural, and economic (SBE) sciences} have been developing and using a
metadata standard (composed of almost twelve hundred metadata fields) known as the \emph{Data Documentation Initiative (DDI)} \cite{Vardigan2008}.
\emph{DDI} is an XML format designed to support the dissemination, management,
and reuse of the data collected and archived for research purposes.  
%DDI is heavily used by the CESSDA community of European national data archives, 
%the International Household Survey Network community (made up of more than 90 statistical agencies),
%and ICPSR - the largest SBE data archive in the US.
Increasingly, data professionals, data archives, data libraries, government statisticians (e.g. \url{data.gov}, \url{data.gov.uk}), and national statistical institutes
are very interested in having their data be discovered and used by providing their metadata (e.g. about unemployment rates or income) on the web in form of RDF.
Recently, members of the SBE and Linked Data community developed the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}, 
an effort to leverage the mature DDI metadata model for the purposes of exposing DDI metadata as resources within the Web of Linked Data.

@@

The main \textbf{contribution} of this paper is the development of a system 
\begin{enumerate}
	\item to classify RDF constraints to evaluate the quality of metadata and data which may be represented by any vocabulary and 
	\item to classify RDF constraint types which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (section \ref{classification} - \ref{complex-constraint-types}).
\end{enumerate}
By defining a huge amount of constraints of different constraint types,   
we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove the generality of the proposed classification system.
A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
how data in tabular format (expressed by the \emph{PHDD} vocabulary) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), and thesauri (\emph{SKOS}) are represented in RDF, and how therefore reused vocabularies are interrelated (section \ref{rdf-representation}).
We explain how \emph{SBE} (meta)data is validated against constraints, instantiated from constraint types organized in the classification system, to ensure high quality of and trust in (meta)data.

>>>>

\begin{abstract}
For research institutes, data libraries, and data archives,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world.
%The data most often used in research within the community around research data for the social, behavioural, and economic sciences (\emph{SBE}) is person-level data, i.e., data collected about individuals (households, businesses). 
%%The DDI-RDF Discovery Vocabulary is used to describe and to discover this kind of research data.
%While performing research, the detailed, often access restricted person-level
%data is aggregated into less confidential publicly available multi-dimensional tables which answer particular research questions and whose purpose is to gain an interest in further more detailed analyses on the underlying person-level data.
To ensure high quality and trust, both metadata and data must satisfy certain criteria - specified in terms of RDF constraints. 
%From 2012 to 2015 together with other Linked Data community members and \emph{SBE} experts, we developed diverse vocabularies to represent \emph{SBE} metadata and data in RDF.

The \textbf{contribution} of this paper is the development of a system 
(1) to classify RDF constraints to evaluate the quality of (meta)data which may be represented by any vocabulary and 
(2) to classify RDF constraint types which in most cases correspond to RDF validation requirements.
By defining a huge amount of constraints of the majority of constraint types
to validate data sets from the community around research data for the \emph{social, behavioural, and economic (SBE) sciences},  
%we apply the developed classification system to several and different vocabularies from the community around research data for the \emph{social, behavioural, and economic (SBE) sciences} in order to
we prove the claim that the developed classification system perfectly applies vocabulary-independent and therefore to prove the generality of the proposed classification system.

We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple and different vocabularies to get an understanding 
(1) which sets of constraint types and 
(2) which sets of constraints (associated with particular severity levels) encompass the most/fewest violated constraints.

\keywords{RDF Validation, RDF Constraints, Metadata Quality, Data Quality, Tabular Data, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, SKOS, Thesauri, Linked Data, Semantic Web}
\end{abstract}

@@

%\tb{terminology: data in singular form / data set - NOT dataset / person-level data - NOT microdata / study - NOT survey}
\tb{metadata on person-level or more generally record-unit data sets (i.e., data about individuals, households, businesses)}
\tb{DCAT und XKOS nur in future work}
For more than a decade, members of the community around research data for the \emph{social, behavioural, and economic (SBE) sciences} have been developing and using a
metadata standard (composed of almost twelve hundred metadata fields) known as the \emph{Data Documentation Initiative (DDI)} \cite{Vardigan2008}.
\emph{DDI} is an XML format designed to support the dissemination, management,
and reuse of the data collected and archived for research purposes.  
%DDI is heavily used by the CESSDA community of European national data archives, 
%the International Household Survey Network community (made up of more than 90 statistical agencies),
%and ICPSR - the largest SBE data archive in the US.
Increasingly, data professionals, data archives, data libraries, government statisticians (e.g. \url{data.gov}, \url{data.gov.uk}), and national statistical institutes
are very interested in having their data be discovered and used by providing their metadata (e.g. about unemployment rates or income) on the web in form of RDF.
Recently, members of the SBE and Linked Data community developed the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}, 
an effort to leverage the mature DDI metadata model for the purposes of exposing DDI metadata as resources within the Web of Linked Data.

@@

The \textbf{contribution} of this paper is the development of a system 
\begin{enumerate}
	\item to classify RDF constraints to evaluate the quality of metadata and data which may be represented by any vocabulary and 
	\item to classify RDF constraint types which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (section \ref{classification} - \ref{complex-constraint-types}).
\end{enumerate}
By defining a huge amount of constraints of different constraint types,   
we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove the generality of the proposed classification system.
A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
how data in tabular format (expressed by the \emph{PHDD} vocabulary) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), and thesauri (\emph{SKOS}) are represented in RDF, and how therefore reused vocabularies are interrelated (section \ref{rdf-representation}).
We explain how \emph{SBE} (meta)data is validated against constraints, instantiated from constraint types organized in the classification system, to ensure high quality of and trust in (meta)data.
